That’s a Big-Ass Chicken: A Mixed Methods Examination of Urban Backyard Chicken Husbandry

### 2025-03-06 BAC_Manuscript_Final.qmd
BAC

## Eggs

>>>>

## Eggs 
```{recho=FALSE, include=FALSE}
#| label: data_analysis_2
Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")
head(Egg_Size)
```

```{recho=FALSE, include=FALSE}
# Step 1: Install and load the dplyr package (if not installed)
# install.packages("dplyr") # this if you haven't installed dplyr
library(dplyr)

# Step 2: Load the data
Egg_Size <- read.csv("Data_BigAssChicken/GallusGallusDomesticus.csv")

# Step 3: Select relevant columns
Egg_Size <- Egg_Size[, c("GallusBreed", "GallusEggWeight", "GallusWeight")]

# Step 4: Remove rows with missing values
Egg_Size <- na.omit(Egg_Size)

# Step 5: Arrange the data by EggWeight in ascending order
Egg_Size <- Egg_Size %>%
  arrange(GallusEggWeight)

# Step 6: Save the cleaned and sorted data to a new CSV file
write.csv(Egg_Size, "Egg_Size_Data.csv", row.names = FALSE)

# Step 7: View the cleaned and sorted data
head(Egg_Size)

```{r}
